---
title: "Statistical Inference Course Project Part 1"
author: "Shun-Wen Chang"
date: "October 24, 2015"
output: pdf_document
---

##Overview:##
This project investigates the exponential distribution in R and compare it with the Central Limit Theorem.

##Simulations:##
The exponential distribution can be simulated in R with rexp(n, lambda) where lambda is the rate parameter. The mean of exponential distribution is 1/lambda and the standard deviation is also 1/lambda. Set lambda = 0.2 and number to average is 40. I do a thousand simulations.

```{r,echo=TRUE}
lambda = 0.2
n = 40
nSim = 1:1000
set.seed(200)
Means <- data.frame(x = sapply(nSim, function(x) {
    mean(rexp(n, lambda))
}))
```
##Sample Mean versus Theoretical Mean:##
```{r,echo=TRUE}
s_mean<-mean(Means$x)
s_mean
t_mean<-(1/lambda)
t_mean
```
The sample mean is almost the same as the theoretical mean with 0.016 difference.

##Sample Variance versus Theoretical Variance:##
```{r,echo=TRUE}
s_var<-var(Means$x)
s_var
t_var<-((1/lambda)/sqrt(n))^2
t_var
```
The sample variance is almost the same as the theoretical variance with 0.033 difference.

##Distribution:##
```{r,echo=TRUE}
library(ggplot2)
ggplot(data=Means,aes(x=x))+geom_histogram(aes(y=..density..),fill="green",binwidth=0.1,color="grey")+stat_function(fun=dnorm,args=list(mean=5,sd=sd(Means$x)))
```

Yes the distribution is approximately normal.
